---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# covidrecon

<!-- badges: start -->
[![DOI](https://zenodo.org/badge/248728805.svg)](https://zenodo.org/badge/latestdoi/248728805)
<!-- badges: end -->

R tools for monitoring effectiveness of COVID-19 control efforts

## Installation

The development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("CBDRH/covidrecon")
```

## Why Another COVID19 R package?

We created an [open source dashboard](https://cbdrh.github.io/ozcoviz/) to combine value-adding data visualisations with updated statistical analysis not yet widely seen. We decided to package up a lot of the code used in the dashboard into this R package.

Now, there are many other R packages for pulling COVID19 data, so why create another one? A few reasons. The main one being that the COVID9 data formats, and other other R packages are changing rapidly. We wanted to perform statistical analysis that aren't widely available. We needed to ensure the data stayed in a format that was easily usable for our purposes. We needed something that we could control and add features to ourselves, that wouldn't need to rely on from another person.

This package is still changing and evolving, and it's primary purpose is to implement code

## Usage

`covidrecon` is designed to add statistical analysis and data visualisations of covid19 data. It was created to power [this dashboard](https://cbdrh.github.io/ozcoviz/).

### Pulling data

The data source that we recommend using is from the European CDC. You can get this data with `covid_latest()`. This will by default cache the data downloaded for that day. Here is what the data looks like.

```{r covid-ecdc}
library(covidrecon)
covid <- covid_latest()
covid
```

This contains new names for the data (from European CDC)

- dateRep --> date_rep
- countriesAndTerritories --> countries_and_territories
- geoId --> geo_id
- countryterritoryCode --> countryterritory_code
- popData2018 --> pop_data2018


For full use of the package and the data visualisations, we recommend that you look at the dashboard, [`ozcovis`](https://cbdrh.github.io/ozcoviz/).

